SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 related.tex
minor stuff

%Two widely used prefetchers are Next-$n$ Lines~\cite{nextn} and
%Stride~\cite{stride} prefetchers. Both capture regular memory access patterns
%with low overhead. The Next-$n$ Lines prefetcher queues prefetches for the
%next $n$ blocks after any given miss, expecting that the principle of spatial
%locality will hold and those cache blocks after a missed block are likely to
%be used in the future. The stride prefetcher identifies strided reference
%patterns in programs based on past behavior of missing loads.  When a load
%misses, cache blocks ahead of that miss are fetched in the pattern following
%the previous behavior in the hope of avoiding future misses.  Without further
%knowledge about temporal locality and application characteristics, these
%prefetchers cannot do more than detecting and prefetching regular memory
%access patterns with limited spatial locality.

Spatial prefetchers include such well-understood examples as the next-line (or
next-$n$-line) prefetcher, and the stream prefetcher, and are distinguished by prefetching
data without regard for the order in which the data will be accessed.
In addition to simpler these, Somogyi \textit{et al.} 
propose Spatial Memory Streaming (SMS)~\cite{SMS}. SMS works by learning
the spatial footprint of all data used by a program within a region of memory,
and when that region is revisited by the program, the same spatial footprint
is prefetched. Ishii \textit{et al.} propose the Access Map Pattern Matching 
prefetcher (AMPM)~\cite{AMPM}, which creates a map of all accessed lines within a region
of memory, and then analyzes this map on every access to see if any 
fixed-stride pattern can be identified and prefetched that is centered on 
the current access. DRAM-Aware AMPM (DA-AMPM)~\cite{DA_AMPM}
is a variant of AMPM that delays some prefetches so they can be issued 
together with others in the same DRAM row, increasing bandwidth utilization.
Pugsley \textit{et al.} propose the Sandbox Prefetcher~\cite{Sandbox},
which analyzes candidate fixed-offset prefetchers in a sandboxed environment
to determine which is most suitable for the current program phase. Michaud
proposes the Best-Offset Prefetcher~\cite{BOP}, which determines the optimal
offset to prefetch while considering memory latency and prefetch timeliness.

@@

Peled \textit{et al.} introduce interesting ideas for on-line Reinforcement
Learning and dynamically scaling the magnitude of feedback given to the
baseline prefetcher~\cite{Semantics}. The prefetcher relies on compiler
support for getting features to build the context. Liao \textit{et al.}
focuse on prefetching for data center applications~\cite{Datacenter}. They
use offline machine learning algorithms such as SVMs and logistic regression
to do a parametric search for an optimal prefetcher configuration.

>>>>

% Two widely used prefetchers are Next-$n$ Lines~\cite{nextn} and
% Stride~\cite{stride} prefetchers. Both capture regular memory access
% patterns with low overhead. The Next-$n$ Lines prefetcher queues
% prefetches for the next $n$ blocks after any given miss, expecting
% that the principle of spatial locality will hold and those cache
% blocks after a missed block are likely to be used in the future. The
% stride prefetcher identifies strided reference patterns in programs
% based on past behavior of missing loads.  When a load misses, cache
% blocks ahead of that miss are fetched in the pattern following the
% previous behavior in the hope of avoiding future misses.  Without
% further knowledge about temporal locality and application
% characteristics, these prefetchers cannot do more than detecting and
% prefetching regular memory access patterns with limited spatial
% locality.

Spatial prefetchers include such well-understood examples as the
next-line (or next-$n$-line) prefetcher, and the stream prefetcher,
and are distinguished by prefetching data without regard for the order
in which the data will be accessed.  In addition to these simpler
examples, Somogyi \textit{et al.}  propose Spatial Memory Streaming
(SMS)~\cite{SMS}.  SMS works by learning the spatial footprint of all
data used by a program within a region of memory around a given
missing load, and when the load that causes an new miss elsewhere, the
same spatial footprint is prefetched.  Ishii \textit{et al.} propose
the Access Map Pattern Matching prefetcher (AMPM)~\cite{AMPM}, which
creates a map of all accessed lines within a region of memory, and
then analyzes this map on every access to see if any fixed-stride
pattern can be identified and prefetched that is centered on the
current access. DRAM-Aware AMPM (DA-AMPM)~\cite{DA_AMPM} is a variant
of AMPM that delays some prefetches so they can be issued together
with others in the same DRAM row, increasing bandwidth utilization.
Pugsley \textit{et al.}  propose the Sandbox
Prefetcher~\cite{Sandbox}, which analyzes candidate fixed-offset
prefetchers in a sandboxed environment to determine which is most
suitable for the current program phase.  Michaud proposes the
Best-Offset Prefetcher~\cite{BOP}, which determines the optimal offset
to prefetch while considering memory latency and prefetch timeliness.

@@

Peled \textit{et al.} introduce interesting ideas for on-line
Reinforcement Learning and dynamically scaling the magnitude of
feedback given to the baseline prefetcher~\cite{Semantics}. The
prefetcher relies on compiler support to receive features and build
the context.  Liao \textit{et al.}  focus on prefetching for data
center applications~\cite{Datacenter}.  They use offline machine
learning algorithms such as SVMs and logistic regression to do a
parametric search for an optimal prefetcher configuration.
